|

### 2025-02-18 docs/presentation.qmd
new paper version

---
title: |
  | How does the Accounting Research Community 
  | Think About Open Science?
subtitle: "" # we use this for the venue
author: Joachim Gassen, Jacqueline Klug, and Victor van Pelt
institute: "HU Berlin and WHU – Otto Beisheim School of Management"
date: today
date-format: "MMMM D, YYYY"
format: 
  beamer:
    latex_engine: xelatex # pdflatex creates rastered fonts
    slide_level: 3

@@

```{r Figure2, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
mr$sharing_important_rescaled = floor(mr$sharing_important)
p <- likert_plot(mr, "sharing_important_rescaled", "demog_discipline", title_str = "To what extent do you believe that publicly sharing research materials is important?", llevels = vars$resp_label[49:53]) +
	theme(legend.text = element_text(size = 6))
if (trr266_fonts_available) {
	p + theme(
		text = element_text(family = "Calibri Light", size = 7),
		legend.text = element_text(size = 6)
	)
} else p + theme(legend.text = element_text(size = 6))

>>>>

---
title: |
  | How Does the Accounting Research Community 
  | Think About Open Science?
subtitle: "" # we use this for the venue
author: Joachim Gassen, Jacqueline Klug, and Victor van Pelt
institute: "HU Berlin and WHU – Otto Beisheim School of Management"
date: today
date-format: "MMMM D, YYYY"
format: 
  beamer:
    latex_engine: xelatex # pdflatex creates rastered fonts
    slide_level: 3

@@

```{r Figure2, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
p <- likert_plot(mr, "sharing_important", "demog_discipline", title_str = "To what extent do you believe that publicly sharing research materials is important?", llevels = vars$resp_label[49:53]) +
	theme(legend.text = element_text(size = 6))
if (trr266_fonts_available) {
	p + theme(
		text = element_text(family = "Calibri Light", size = 7),
		legend.text = element_text(size = 6)
	)
} else p + theme(legend.text = element_text(size = 6))
